%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

%------------
\usepackage{enumitem}
\renewenvironment{entrylist}{%
  \begin{itemize}[leftmargin=1in]%[leftmargin=*,align=left,itemindent=-\dimexpr\labelwidth+\labelindent+\labelsep\relax]
}{%
  \end{itemize}
}
\renewcommand{\bfseries}{\headingfont\color{headercolor}}
\renewcommand{\entry}[4]{%
  \item[#1]
    \textbf{#2}%
    \hfill%
    {\footnotesize\addfontfeature{Color=lightgray} #3}\\%
    #4\vspace{\parsep}%
  }
%-------

\begin{document}

\header{Hamilton Daniel}{Cesario}{SysOps Engineer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Xifrè, 2 1-2
Barcelona, Barcelona 08026
Spain
~
+34 664 174 101
Skype id: daniel.cesario
~
\href{mailto:hdcesario@me.com}{hdcesario@me.com}
\href{http://es.linkedin.com/in/dcesario/}{linkedin://in/dcesario}
\href{https://github.com/maneta}{github://maneta}
\section{languages}
Portuguese mother tongue
English \& Spanish fluency
\section{programming}
{\color{red} $\varheartsuit$} Perl, Bash, PowerShell, Python, Ruby. 
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}
\begin{entrylist}

%------------------------------------------------
\entry
{2014--Now}
{CAPSiDE}
{Barcelona, Spain}
{\emph{SysOps Engineer} 
\begin{itemize}[label=\textbullet]
    \item \href{http://www.fcbarcelona.com/}{\textbf{FC Barcelona}} Web Plataform Migration, LFP Ticketing system implementation, Mobile API Caching, SQL Server Always On (AWS). 
\item \href{http://kelvinretail.com/}{\textbf{Banc Sabadell Kevin}} Azure Resource Manager architecture, Mongo DB Replica Set, Red/Black Deploy System.
\item \href{http://www.tmb.cat/}{\textbf{TMB}} Liferay based platform on Auto Scaling, ELK Stack Cluster, JBoss Backed system.
\item \href{http://www.sidetours.com/}{\textbf{Sidetours}} Cloud Infrastructure, MySQL Replication System on Auto Scaling automation.
\item \href{http://www.elpuntavui.cat/}{\textbf{El Punt Avui}} Migration from Virtual Datacenter to Azure, MySQL Galera Cluster Implementation, Full Configuration management with Ansible.
\item \href{https://www.saludonnet.com/}{\textbf{Salud On Net}} Azure IAAS ARM formation..
\item \href{http://www.prisa.com/}{\textbf{Grupo Prisa}} Cloud DevOps Consultancy.
\item AWS Advanced Solution Architect Oficial Course.  
\item AWS Solution Architect Certification. 
\item Azure for AWS profesionals Oficial Course. 
\item AWS Solution Architect Certification. 
\item Cloud and System Automation Development for multiple purposes, mostly in Perl.
\item Last OSS projects contributions: \href{https://github.com/Azure/azure-quickstart-templates}{\textbf{Azure ARM Templates}}, \href{https://github.com/pplu/aws-sdk-perl}{\textbf{Perl AWS SDK}}, \href{https://github.com/RexOps/Rex}{\textbf{RexOps Configuration Management System}}.
\end{itemize}}
%------------------------------------------------
%------------------------------------------------

\entry
{2014--2014}
{Opscaling}
{Barcelona, Spain}
{\emph{SysOps Engineer} 
\begin{itemize}[label=\textbullet]
\item \href{http://www.fcbarcelona.com/}{\textbf{FC Barcelona}} Cloud Infrastructure Management, Continuous Integration Implementation via git and Puppet, Auto Scaling Enhancements, Web Performance enhancements via CloudFront, S3, Varnish and Nginx.
\item \href{http://www.bdigital.org/}{\textbf{Barcelona Digital}} Big Data Technical consultancy and Automation on Elastic Map Reduce, Hive, GIS Tools for elastic Map Reduce and Spark.
\item \href{http://www.tuitele.tv/}{\textbf{Tuitele}} Big Data Technical consultancy on Elastic Map Reduce, EC2 cluster scalability and automatization on cluster deployment.
\item \href{http://www.lavanguardia.com/}{\textbf{La Vanguardia}} Cloud Infrastructure, Configuration and System Management, Platform monitorization and Web Performance Enhancements.
\item \href{http://www.aedgency.com/}{\textbf{Aedgency Performance-Based Marketing}} Configuration, System Management, Platform monitorization on a highly automated and complex infrastructure.
\item Cloud and System Automation Development for multiple purposes, mostly in Python.   
\end{itemize}}
%------------------------------------------------
\entry
{2012--2014}
{AppBridge Inc.}
{Barcelona, Spain}
{\emph{Solution Architect} 
\begin{itemize}[label=\textbullet]
\item \href{http://www.appbridge.com}{\textbf{AppBridge}} Project Design, Product Management, Cloud Architecture team leadership.
\item Lead Perl core development team for the product \href{http://www.ebdsoft.com}{\textbf{eBD Web Application Development Platform}}, implementing scrum agile techniques, bringing the platform: new security modules, web rendering optimization system,Apache \& MySQL version update, new look \& feel and a new code editor.
\item Private Cloud design and automation for the  \href{http://www.ebdcloud.com}{\textbf{eBDCloud}} PAAS Product (CloudStack, Xenserver, Puppet, CentOS).
\item Architecture and Scalable Design for the Social Networking \href{http://www.fangazing.com/berto}{\textbf{Fangazing}}.
\item Architecture and Scalable Design for the the \href{https://webstore.telefonicaglobalsolutions.com}{\textbf{Webstore Telefonica Global Solutions}}
\item Technical Consultancy to eBD Web Application Development Platform clients, such as \textbf{Mapfre Florida}, \textbf{Telefonica Global Solutions}, \textbf{Grupo Serhs} \& \textbf{Servei Català de Transit}.
\item System Script development for multiple purposes, mostly Python and Perl.   
\end{itemize}}
%------------------------------------------------
\entry
{2010--2012}
{UPC Universitat Politènica de Catalunya}
{Barcelona, Spain}
{\emph{Junior SysOps} 
\begin{itemize}[label=\textbullet]
\item Perl Developer at the \href{https://github.com/smeagol-upc/smeagol-perl}{\textbf{Smeagol Project}}.
\item LDAP UPCnet Integration.
\item Samba Virtual File System Implementation.
\item Network and System Administration Tasks.
\item System Script development for multiple purposes, mostly Perl
\end{itemize}}
%------------------------------------------------
\end{entrylist}

\section{previous experience}
\begin{entrylist}
\entry
{2008-2010}
{CPET S.C.C.L}
{Barcelona, Spain}
{\emph{I.T Manager} 
\begin{itemize}[label=\textbullet]
\item Debian, LAMP, OpenVPN System Administration.
\item Networking Administration for a distributed photocopier self service system at the \textbf{UPC Universitat Politènica de Catalunya}.
\item Implementation of a distributed remote OS recovery system.
\item Implementation of a unified print quote system for the departments and students of the university.
\item Software and Hardware negotiation and consultancy for investigation departments at the \textbf{UPC Universitat Politènica de Catalunya}.
\item System Script development for multiple purposes, mostly Perl and Bash.
\end{itemize}}
%------------------------------------------------

\entry
{2005-2007}
{Netron ISP}
{Blumenau, Brazil}
{\emph{Junior System Administrator} 
\begin{itemize}[label=\textbullet]
\item FreeBSD LAMP system Administration.
\item Networking Administration for RADIUS systems.
\item System Script development for multiple purposes, mostly Bash.
\end{itemize}}
%------------------------------------------------

\end{entrylist}
%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------
\section{professional skills}
{\large \textbf{Cloud Computing:}}
\begin{itemize}
\item Amazon Web Services, Microsoft Azure.   
\end{itemize}
{\large \textbf{System Administration:}}
\begin{itemize}
%ToDo: Redefine the System Administration section
\item Unix(RH,Debian,MacOS \& FreeBSD Based Systems), Configuration Management Tools (Ansible, Puppet), Version Control Systems (Git, SVN), Xenserver, VM Ware ESX, Nagios, Cacti, MySQL, MongoDB, Apache, Nginx, lvm ,ffmpeg/avconv, mod\_pagespeed, \\ 
Varnish,mod\_security, mod\_evasive, iptables, DNS, Zimbra, qmail,dhcpd, DNS, LDAP, Samba, mod\_perl, mod\_php, fastcgi, HAProxy, squid, Wireshark \& pound.  
\end{itemize}
{\large \textbf{Big Data:}}
\begin{itemize}
\item Hadoop, Hive, Spark, \& Elastic Map Reduce.   
\end{itemize}
%ToDo: Redefine the Networking stak to more cloudish technologies
{\large \textbf{Networking:}}
\begin{itemize}
\item Layer 7 Protocols: HTTP, HTTPS, FTP, SSH, SMTP/POP, Telnet, IRC, RTMP, RTMPT, BGP, RTP, RTSP, SAMBA, DNS, IMAP, LDAP, NTP \& SIP. 
\item Layer 4 Protocols: TCP, UDP, GRE, AH \& SCTP.
\item Layer 3 Protocols: IPv4, IPv6, IPSec, IGMP, ARP,OSPF, RIP, ICMP, AH, SDH \& SCTP.
\item Layer 2 Protocols: Ethernet, 802.11, PPP, PPTP, STP \& VTP.
\end{itemize}
%ToDo: Update the last developments 
{\large \textbf{Software Development:}}
\begin{itemize}
\item Script Crafting,Data Modeling, RESTful API Design and Development, Capistrano, Boto Interface Development, Catalyst, Mojolicious, Bottle, Mason,SQL, NoSQL, System modeling,MVC, Scrum, Git, SVN \& VIM.
\end{itemize}
{\large \textbf{Managerial:}}
\begin{itemize}
\item Project Management, strong written and verbal communications, solution orientation, experience in multinational environments, team player  \& effective presentation skills. 
\end{itemize}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2009--Now}
{Degree {\normalfont of Telematics Engineer}}
{UPC - Universitat Politecnica de Catalunya}
{Specialization in Network Protocols and Software Development}
%------------------------------------------------
\entry
{2001--2007}
{Bachelor {\normalfont of Telecommunication Engineer}}
{Furb -  Universidade Regional de Blumenau}
{Specialization in Telecommunication Systems}
%------------------------------------------------
\end{entrylist}
%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} Unix, Open Source, Infrastructure Orchestration, IT Security, Cloud Computing, Network Protocols, Virtualization, Big Data,Design Patterns, Databases, Web Applications Design, API Design \& Agile Team Management \\ 
\textbf{personal:} Music, Bass Playing, Cooking, Beer, Wine \& Technology 
%----------------------------------------------------------------------------------------

\end{document}
